Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-06 tex/paper1/paper1.tex
paper edits

Time series of AIA 171\AA\ and 193\AA images show approximately power
law like properties over all regions of the solar surface.  The power
spectra have been modelled using a power-law power spectrum with a
constant background summed with a localized contribution

>>>>

Time series of AIA 171\AA\ and 193\AA images show approximately power
law like properties over all regions of the solar surface.  Detecting
narrow band oscillatory power should take in to account the presence
of the power-law like power spectrum.  The power spectra have been
modelled using three components: a power-law power spectrum, a
lognormal component, and a constant background.  It is hypothesized
that the power-law component is due to the sum along the line of sight
of a large number of statistically similar energy deposition events.
It is also hypothesized that the lognormal component is due to the
channeling of oscillatory power from lower to higher levels of the
solar atmosphere.
